---
title: "Complex Function Plot"
author: "Gian Arjuna"
date: "December 24, 2018"
output:
  #slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn=-1)
```

##Complex Function Plot with plotly
- In this slide we will plot a complex function using plotly library
- The algorithm can plot function for power with natural numbers

##Load Library and Create Data
- The real domain of the function is between -10 and +10
- The imaginary domain of the function is between -10i and +10i

```{r, include = FALSE}
library(plotly)
```
```{r}
#create the domain
x <- seq(-10,10, length = 21)
iy <- seq(-10i,10i, length = 21)
f <- function(x,iy){
    z <- matrix(nrow = length(x), ncol = length(iy))
    for(i in 1:length(x)){
        for(j in 1:length(iy)){
            z[i,j] <- x[i]+iy[j]
        }
    }
    return(z)
}
z <- f(x,iy)
``` 

##Calculate The Function Output 
- Next we create the function and calculate its output
- Then we extract the real and imaginary part of the function
- In the next slide the plot of the function will be shown
```{r}
#calculate the function
fz <- z^4

#extract the real and imaginary part of the function
fx <- Re(fz)
fiy <- Im(fz)
```

##Plot The Real Part of The Function
```{r, echo = FALSE}
plot_ly(z = fx, type = "surface")
```

##Plot The Imaginary Part of The Function
```{r, echo = FALSE}
plot_ly(z = fiy, type = "surface")
```

#Thank you